Estimating duration in the presence of misclassification

### 2024-03-07 introduction.tex
Overleaf comments

The coronavirus disease 2019 (COVID-19) caused by the Ssevere acute respiratory syndrome coronavirus 2 (SARS-CoV-2), is estimated to have killed approximately 15 million in the acutest phase (to the end of 2021) and 30 million globally~\autocite{whoCOVIDExcess,economistCOVIDExcess}.
While it is tempting to consider this a rare or extreme event, history suggests otherwise (see \cref{intro:fig:pandemic-timeline}).
\begin{figure}
    \includegraphics[width=\textwidth]{introduction/pandemic-timeline}
    \caption[Timeline of pandemics.]{%
        Timeline of pandemics.
        See \url{https://ourworldindata.org/historical-pandemics} for details and sources.
        Licensed under \href{https://creativecommons.org/licenses/by/4.0/}{CC-BY} by Saloni Dattani, Klara Auerbach, Marwa Boukarim, and Max Roser.
    }
    \label{intro:fig:pandemic-timeline}
\end{figure}

@@

To translate incidence into the burden of the disease, a measure of severity is required.
For example, the infection fatality rate (IFR), the proportion of infected individuals who die.
Estimation of severity is beyond the scope of this thesis.
% Severity does not feature in this thesis, but it is important to note that it is a key component of understanding the burden of a pandemic.\todo{maybe reword sentence}

@@

Community testing is broadly available, but does not test a random sample of the population.
The number of tests conducted varies over time and space, for a variety of known and unknown reasons.
These include: policy on who is eligible for testing, the availability of tests, and the willingness of individuals to be tested.
Therefore, fluctuations in the number of positive tests may not reflect changes in the true incidence of the disease.
For large parts of the pandemic, community testing was widely available in the UK meaning resulting in a rich dataset, allowing detailed analyses to be performed, including stratification by small geographic areas or age groups.

@@

The use of prevalence surveys for estimating incidence and transmission is the focus of this thesis.
In particular, I focus on the Coronavirus (COVID-19) Infection Survey (CIS ), run by the Office for National Statistics (ONS)~\autocite{CIS,cisMethodsONS}.
The CIS was a longitudinal study, testing a large number of indidividuals weekly or monthly for SARS-CoV-2; it is described in detail in \cref{E-intro:sec:cis}.
Early in the pandemic, a methodology was developed for using CIS data to estimate prevalence (see \cref{E-intro:sec:cis}).
The primary aim of this thesis is to estimate incidence and transmission from this data.

>>>>

COVID-19 (coronavirus disease 2019), the disease caused by the virus SARS-CoV-2 (severe acute respiratory syndrome coronavirus 2), is estimated to have killed approximately 15 million in the acutest phase (to the end of 2021) and 30 million globally~\autocite{whoCOVIDExcess,economistCOVIDExcess}.
While it is tempting to consider this a rare or extreme event, history suggests otherwise (see \cref{intro:fig:pandemic-timeline}).
\begin{figure}
    \includegraphics[width=\textwidth]{introduction/pandemic-timeline}
    \caption[Timeline of pandemics.]{%
        Timeline of pandemics.
        See \url{https://ourworldindata.org/historical-pandemics} for details and sources.
        Licensed under \href{https://creativecommons.org/licenses/by/4.0/}{CC-BY} by Saloni Dattani, Klara Auerbach, Marwa Boukarim, and Max Roser.
    }
    \label{intro:fig:pandemic-timeline}
\end{figure}

@@

To translate incidence into the burden of the disease, a measure of severity is required.
For example, the IFR (infection fatality rate), the proportion of infected individuals who die.
Estimation of severity is beyond the scope of this thesis.
% Severity does not feature in this thesis, but it is important to note that it is a key component of understanding the burden of a pandemic.\todo{maybe reword sentence}

@@

Community testing is broadly available, but does not test a random sample of the population.
The number of tests conducted varies over time and space, for a variety of known and unknown reasons.
These include: policy on who is eligible for testing, the availability of tests, and the willingness of individuals to be tested.
Therefore, fluctuations in the number of positive tests may not reflect changes in the true incidence of the disease.
For large parts of the pandemic, community testing was widely available in the UK meaning that this is a large dataset, allowing detailed analyses to be performed, including stratification by small geographic areas or age groups.

@@

The use of prevalence surveys for estimating incidence and transmission is the focus of this thesis.
In particular, I focus on the CIS (Coronavirus (COVID-19) Infection Survey), run by the Office for National Statistics (ONS)~\autocite{CIS,cisMethodsONS}.
The CIS was a longitudinal study, testing a large number of indidividuals weekly or monthly for SARS-CoV-2; it is described in detail in \cref{E-intro:sec:cis}.
Early in the pandemic, a methodology was developed for using CIS data to estimate prevalence (see \cref{E-intro:sec:cis}).
The primary aim of this thesis is to estimate incidence and transmission from this data.
